---
title: "Dataset_description"  
output: html_document  
date: "2024-09-18"  
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

## Dataset Description

The dataset in *psychopy_dataset.RData* contains information about various attributes of a study involving participants, their responses, and video stimuli. The data is collected from experiments that focus on emotion authenticity discrimination and intensity judgment tasks.

### Loading the Dataset

To load the dataset into R, you can use the following code:

```{r , echo=TRUE, eval = FALSE}
# Load the dataset
load("data/psychopy_dataset.RData") 

```

### PEDFE videoclips info columns

1. **File.name**:  
   - Variable: `File.name`  
   - Description: The filename of the PEDFE video clip shown during the experiment.  
   - Type: Character  

2. **File.emotion**:  
   - Variable: `File.emotion`  
   - Description: The emotion depicted in the video clip (e.g., Anger, Happiness, Fearfull).  
   - Type: Factor  

3. **File.elicitation**:  
   - Variable: `File.elicitation`  
   - Description: The method used to elicit the emotion, categorized as "genuine" or "paused."  
   - Type: Character  
   
### Participant Columns

4. **Pt.id**:  
   - Variable: `Pt.id`  
   - Description: Identifier for the participant.  
   - Type: Numeric  

5. **Pt.age**:  
   - Variable: `Pt.age`  
   - Description: Age of the participant.  
   - Type: Numeric  

6. **Pt.gender**:  
   - Variable: `Pt.gender`  
   - Description: Gender of the participant.  
   - Type: Character  

7. **Pt.ccPAS**:  
   - Variable: `Pt.ccPAS`  
   - Description: Categorical data indicating TMS conditions.  
   - Type: Character  

8. **Pt.group**:  
   - Variable: `Pt.group`  
   - Description: Group assignment, indicating specific experimental groups.  
   - Type: Factor  

### Authenticity Emotion Discrimination (AED) Task Columns

9. **AED.accuracy**:  
   - Variable: `AED.accuracy`  
   - Description: Whether the key response was correct (1) or not (0) in the AED task.  
   - Type: Integer  

9. **AED.resp**:  
   - Variable: `AED.resp`  
   - Description: The key response in the AED task.  
   - Type: Character  
   
10. **AED.intensity**:  
   - Variable: `AED.intensity`  
   - Description: Response value recorded on the "genuine" slider task.  
   
### Emotion Intensity Judgment task (EIJ) Columns

11. **EIJ.accuracy**:  
   - Variable: `EIJ.accuracy`  
   - Description: Measure of accuracy in the emotion recognition task (binomial e.g., 1,0).  
   - Type: int  

12. **EIJ.label**:  
   - Variable: `EIJ.label`  
   - Description: Name of the object (e.g., emotion) clicked by the mouse.  
   - Type: Character  

13. **EIJ.intensity**:  
   - Variable: `EIJ.intensity`  
   - Description: Response value recorded on the "emotion" slider task.  
   - Type: Numeric  

### Technical Setup Columns
14. **Exp.date**:  
   - Variable: `Exp.date`  
   - Description: Date and time when the session was conducted.  
   - Type: Character 
   
15. **Exp.session**:  
   - Variable: `Exp.session`  
   - Description: Type of session, categorizing experimental phases.  
   - Type: Factor 
   
16. **Exp.name**:  
   - Variable: `Exp.name`  
   - Description: Name of the experiment, labeled as "genuine."  
   - Type: Character  

17. **Exp.version**:  
   - Variable: `Exp.version`  
   - Description: Version of PsychoPy used for the experiment.  
   - Type: Character  

18. **Exp.frameRate**:  
   - Variable: `Exp.frameRate`  
   - Description: Frame rate of the experiment's display.  
   - Type: Numeric  

 

